Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-04-17 Paper/paper.tex
Update text

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{siunitx}
\def\lya{Ly$\alpha$~}
\usepackage{color}
\definecolor{notecolor}{rgb}{0.8,0,0}
\newcommand{\gk}[1]{{\bf \color{notecolor} [#1]}}
\def\HI{\hbox{H~$\scriptstyle\rm I$}}
\def\HII{\hbox{H~$\scriptstyle\rm II$}}
\def\nHI{{\rm HI}}
\def\nH{{\rm H}}
\def\nHII{{\rm HII}}
\def\nHe{{\rm He}}
\def\nHeI{{\rm HeI}}
\def\nHeII{{\rm HeII}}
\def\nHeIII{{\rm HeIII}}
\def\bHII{\hbox{\bf H~$\scriptstyle\bf II$}}
\def\HeI{\hbox{He~$\scriptstyle\rm I$}}
\def\HeII{\hbox{He~$\scriptstyle\rm II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\def\bHeII{\hbox{\bf He~$\scriptstyle\bf II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\usepackage{dcolumn}
\newcolumntype{.}{D{.}{.}{2.6}}
\newcolumntype{d}{D{.}{.}{2.3}}

@@

\author[Kulkarni et al.]{{Girish Kulkarni$^{1}$\thanks{Email:
      kulkarni@ast.cam.ac.uk}, G\'abor Worseck$^{2}$ and Joseph
    F.~Hennawi$^{3}$} \\ $^1$Institute of Astronomy and Kavli
  Institute of Cosmology, University of Cambridge, Madingley Road,
  Cambridge CB3 0HA, UK \\ $^2$Institute f\"ur Physik und Astronomie,
  Universit\"at Potsdam, Karl-Liebknecht-Stra\ss e\ 24/25, 14476 Potsdam,
  Germany\\ $^3$Department of Physics, Broida Hall, UC Santa Barbara,
  Santa Barbara, CA 93106-9530 USA}
\date{Accepted ---. Received ---; in original form ---}

@@

\begin{abstract}
We present the evolution UV/optical luminosity function of quasars
from a homogeneous reanalysis of more than 85,000 spectroscopically
selected quasars from redshift $z=0$ to $7.5$.  We derived luminosity
functions when the observed quasar population is binned in luminosity
and redshift, and then construct a continuous evolutionary model of
the luminosity function spanning a range of redshifts.  We find that
quasars selected from the BOSS survey at $z=2$--$3$ show a significant
systematic offset from the general trends, possiblity due to the
colour bias suffered by BOSS.  Some systematic errors also persist in
the lowest-redshift quasar sample due to host galaxy effects. However,
we find that it is possible to describe the luminosity function
evolution from redshift $z=0$ to $7.5$ using a simple 14-parameter
evolving double power law model.  The evolution of the number density
of qsos shows the familiar downsizing effect, although the evolution
in the faint quasar population is quite flat at high redshifts such
that the the drop in their number density at high redshifts is much
slower than that for bright quasars.  When integrated down to
$M_{1450}=-20$ quasars can produce all of the hydrogen-ionizing
photons in the intergalactic medium upto redshifts 3.5.  They fall
short of the emissivity required to explain the Ly$\alpha$ data at
higher redshifts, and are therefore unlikely to have singlehandedly
driven hydrogen reionization.  This conclusion can be altered,
however, if lower luminosity qsos (down to $M_{1450}=-18$) are assumed
to exist and to have a unity escape fraction, in which case qsos can
potentially produce all the hydrogen-ionizing flux at $z<7.5$.
He~\textsc{ii} reionization in this model occurs between $z=3.2$ and
$3.7$.
\end{abstract}

@@

%% * Possible outline of paper:
%% 
%% Introduction 
%% Data
%% Method
%%   Individual fits
%%   Global fits
%% Contribution to reionizatin 
%% Conclusions
%% 
%% * Optional possibilities:
%%
%% Low-z photon under-production
%% Bolometric LF
%% Public code description 
%% More global models: PLE, PDE, Trenti, White-Conroy
%% Goodness of fit 
%% BH growth 
%% Comparison with galaxy LF
%% Comparison with previous work

@@

The luminosity function of active galactic nuclei (AGN) and its
evolution over cosmological time scales has been a matter of central
interest of a large body of work over the last four decades
\citep[e.g.,][]{1978A&A....68...17M, 1983ApJ...269..352S,
  1988ApJ...325...92K, 1988MNRAS.235..935B, 1993ApJ...406L..43H,
  1994ApJ...421..412W, 1995AJ....110...68S, 1995AJ....110.2553K,
  1995ApJ...438..623P, 2000MNRAS.317.1014B, 2001AJ....121...54F,
  2004AJ....128..515F, 2006AJ....131.2766R, 2007ApJ...654..731H,
  2009MNRAS.392...19C, 2010AJ....139..906W, 2011ApJ...728L..26G,
  2013ApJ...773...14R, 2013ApJ...768..105M, 2015AA...578A..83G,
  2015ApJ...798...28K, 2016ApJ...829...33Y, 2016ApJ...833..222J,
  2017MNRAS.466.1160M}.  Determination of the AGN luminosity function
constrains models of the build-up of supermassive black holes
\citep{2015MNRAS.452..575S, 2016MNRAS.462..190R}.  Due to the
incidence of supermassive black holes in most galaxies, the tight
scaling relations observed to exist between the mass of these black
holes and properties of their host galaxies
\citep{2013ARA&A..51..511K, 2013ApJ...764..184M}, and the increasing
consensus that AGN activity feeds back on the host galaxy evolution,
the AGN luminosity function also constrains models of galaxy
formation.  Finally, thanks to their relative brightness and high
Lyman continuum escape fraction, the luminosity function of AGN
determines their influence on the temperature and ionization state of
the intergalactic medium (IGM) over large scales, possibly even
primarily driving hydrogen and helium reionization.

The claimed discovery of 19 low-luminosity ($M_{1450}>-22.6$) AGN
between redshifts $z=4.1$ and $6.3$ by \citet{2015AA...578A..83G}
using a novel X-ray/NIR selection criterion, has renewed the interest
in the evolution of the UV luminosity function of AGN.  This finding
suggested that the faint end of the quasar UV luminosity function is
steeper at these redshifts than previously thought
\citep{2007ApJ...654..731H, 2012ApJ...746..125H}.  Using far-UV
spectral slopes from composite spectra of low-redshift quasars, and
assuming a Lyman continuum escape fraction of 100\%,
\citet{2015AA...578A..83G} argued that AGN brighter than
$M_{1450}=-18$ can potentially produce all of the metagalactic
hydrogen photoionization rate inferred from the \lya forest at
$4<z<6$.  Additional indications of a significant presence of AGN at
high redshift ($z\sim 6$) have emerged.  First,
\citet{2015MNRAS.447.3402B} reported a large scatter in the \lya
opacity between different sightlines close to redshift
$z=6$. \cite{2015MNRAS.453.2943C} showed that these opacity
fluctuations extend to substantially larger scales ($\gtrsim 50\,
h^{-1}$cMpc) than expected in reionization histories dominated by
low-luminosity galaxies (see also \citealt{2016MNRAS.460.1328D}).
\citet{2017MNRAS.465.3429C} further demonstrated that opacity
fluctuations on such large scales arise naturally if there is a
significant contribution ($\gtrsim 50\%$) of AGN to the ionising
emissivity at the redshift of the observed opacity fluctuations ($z
\sim 5.5$--$6$) as would be expected for a QSO luminosity that is
consistent with the measurements of \citet{2015AA...578A..83G}.
Second, measurements of the Lyman continuum escape fraction from
high-redshift galaxies are still elusive.  Although high-redshift
galaxies as faint as rest-frame UV magnitude $M_\mathrm{UV}=-12.5$
($L\sim 10^{-3}L^*$) at $z=6$ \citep{2017ApJ...835..113L} and
redshifts as high as $z=11.1$ \citep{2016ApJ...819..129O} have now
been reported, the escape of Lyman continuum photons has been detected
in only a small number of comparatively bright ($L>0.5L^*$)
low-redshift ($z < 4$) galaxies.  In these galaxies, the escape
fraction is typically found to be 2--20\% \citep{2010ApJ...725.1011V,
  2011ApJ...736...41B, 2015ApJ...804...17S, 2015ApJ...810..107M,
  2016A&A...585A..48G, 2017MNRAS.468..389J, 2017MNRAS.465..316M} but
reionization would require escape fraction of about 20\% in galaxies
down to $M_\mathrm{UV}=-13$ \citep{2016PASA...33...37F,
  2015ApJ...802L..19R, 2016MNRAS.457.4051K}.  Finally, incidence of
high-redshift AGN is also consistent with the shallow bright-end
slopes of the high-redshift ($z\sim 7$) UV luminosity function of
galaxies relative to a Schechter-function representation
\citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B, 2014ApJ...792...76B,
  2015MNRAS.452.1817B} and the hard spectra of these bright galaxies
\citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S, 2017MNRAS.464..469S}.

However, these arguements in favour of a higher incidence of
UV-emitting AGN at high redshit, have been contested by several
observations.  \citet{2016arXiv160706467D} considered the effect of
AGN-dominated reionization on the Ly$\alpha$ opacity at $z>5$,
He~\textsc{ii} Ly$\alpha$ opacity at $z\sim 3.1$--$3.3$, and the
thermal history of the IGM.  In agreement with
\citet{2015MNRAS.453.2943C}, these authors found that AGN did provide
a plausible explanation for the large fluctuations in the Ly$\alpha$
opacity at $z>5$.  However, they found that reionization of
He~\textsc{ii} occurs much earlier in these AGN-dominated models (see
also \citealt{2016arXiv160602719M}).  For instance, in the model of
\citet{2015ApJ...813L...8M}, He~\textsc{ii} reionization is complete
at $z=4.5$, compared to $z=3$ in the standard scenario
\citep{2012ApJ...746..125H}.  This early Helium reionization could
result in higher IGM temperatures due to the associated photoheating.
The temperature of the IGM at mean density is enhanced in
AGN-dominated models by factors of $\sim 2$ relative to the standard
models for $z=3.5$--$5$, in conflict with measurements.  This
inconsistency could be avoided by reducing the escape fraction of 4~Ry
photons in AGN, but it is not clear if this can be achieved while
requiring a 100\% escape fraction of 1~Ry photons in order to explain
the Ly$\alpha$ opacity fluctuations.  Further evidence against
AGN-dominated reionization models has emerged from metal-line
absorbers at $z\sim 6$.  In their cosmological radiation
hydrodynamical simulations, \citet{2016MNRAS.459.2299F} find that the
hard spectral slopes of UV backgrounds in AGN-only reionization models
produce too many C~\textsc{iv} absorption systems relative to
Si~\textsc{iv} and C~\textsc{ii} at $z\sim 6$.  However, these
simulations assume an $L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
\citep{2001AJ....122..549V, 2002ApJ...579..500T, 2012ApJ...746..125H}.
This slope is marginally harder than recent measurements
($L_\nu\propto\nu^{-1.7}$) from a stack of $z\sim 2.4$ quasars
\citep{2015MNRAS.449.4204L}.  \citet{2016MNRAS.459.2299F} also find
that the N(Si~\textsc{iv})/N(C~\textsc{iv}) column density ratio
measurements prefer a somewhat harder and more intense $>4$~Ry
background than the standard model of \citet{2012ApJ...746..125H}.
Using a large sample of X-ray-selected quasars in the redshift range
$z=0$--$6$, \citet{2017MNRAS.465.1915R} find that the faint end of the
AGN UV luminosity function at $z\sim 6$ is likely to be much shallower
that that reported by \citet{2015AA...578A..83G}.  In their analysis,
\citet{2017MNRAS.465.1915R} use an AGN obscuration optical depth
($\log N_\mathrm{H}$) cut-off that reproduces low-redshift AGN UV
luminosity functions and an X-ray-to-optical/UV luminosity ratio
calibrated at redshifts $z=0.05$--$4$ \citep{2010A&A...512A..34L}.
These authors argue that the apparent contradiction with the results
of \citet{2015AA...578A..83G} could be explained by contamination
from the AGN host galaxies.  It has also been recently argued that the
Lyman continuum escape fraction of AGN might not be 100\% as is
usually assumed \citep{2017MNRAS.465..302M}.  This may further reduce
the contribution of AGN to reionization.

@@

\section{Luminosity function}

@@

\begin{table}
  \caption{Best-fit luminosity function evolution models.  These
    parameters are defined in Equations~(\ref{eqn:cbs}) and
    (\ref{eqn:beta}).  See Section~\ref{sec:global} for further
    details and the redshift range of validity of these models.
    Errors indicate one-sigma (68.26\%) uncertainties.  Model 2 is our
    preferred model.}
  \label{tab:global}
  \begin{tabular}{lrrr}
    \hline 
    Parameter & Model 1 & Model 2 & Model 3 \\
    \hline
    $c_{0,0}$ & $-7.559^{+0.131}_{-0.139}$ & $-7.084^{+0.136}_{-0.142}$ & $-6.842^{+0.077}_{-0.076}$ \\     
    $c_{0,1}$ & $1.013^{+0.079}_{-0.072}$ & $0.753^{+0.080}_{-0.073}$ & $0.590^{+0.039}_{-0.041}$ \\        
    $c_{0,2}$ & $-0.113^{+0.005}_{-0.005}$ & $-0.096^{+0.004}_{-0.005}$ & $-0.083^{+0.003}_{-0.003}$ \\
    \\
    $c_{1,0}$ & $-17.006^{+0.230}_{-0.243}$ & $-15.423^{+0.263}_{-0.261}$ & $-15.140^{+0.144}_{-0.136}$ \\  
    $c_{1,1}$ & $-5.548^{+0.156}_{-0.143}$ & $-6.725^{+0.156}_{-0.171}$ & $-6.910^{+0.091}_{-0.093}$ \\     
    $c_{1,2}$ & $0.588^{+0.016}_{-0.019}$ & $0.737^{+0.018}_{-0.015}$ & $0.750^{+0.012}_{-0.013}$ \\        
    $c_{1,3}$ & $-0.023^{+0.001}_{-0.001}$ & $-0.029^{+0.001}_{-0.001}$ & $-0.029^{+0.001}_{-0.001}$ \\
    \\
    $c_{2,0}$ & $-3.246^{+0.121}_{-0.123}$ & $-2.973^{+0.117}_{-0.133}$ & $-2.950^{+0.105}_{-0.097}$ \\     
    $c_{2,1}$ & $-0.250^{+0.048}_{-0.050}$ & $-0.347^{+0.050}_{-0.050}$ & $-0.363^{+0.040}_{-0.043}$ \\
    \\
    $c_{3,0}$ & $-2.350^{+0.051}_{-0.060}$ & $-2.545^{+0.123}_{-0.290}$ & $-1.424^{+0.031}_{-0.031}$ \\     
    $c_{3,1}$ & $0.647^{+0.072}_{-0.060}$ & $1.581^{+0.520}_{-0.264}$ & $-0.111^{+0.010}_{-0.010}$ \\       
    $c_{3,2}$ & $3.857^{+0.092}_{-0.073}$ & $2.102^{+0.450}_{-0.283}$ & --- \\        
    $c_{3,3}$ & $27.534^{+41.364}_{-9.405}$ & $1.965^{+0.461}_{-0.464}$ & --- \\      
    $c_{3,4}$ & $-0.002^{+0.074}_{-0.082}$ & $-0.641^{+0.169}_{-0.154}$ & --- \\      
    \hline 
  \end{tabular}
\end{table}

\section{Contribution of AGN to reionization}

@@

\section{Conclusions}

@@

In spite of the rapid steepening of the faint end of the luminosity
function at high redshifts, our derived hydrogen-ionizing emissivity
from AGN is lower that recent determinations from the literature
\citep{2015AA...578A..83G}.  This is because the bright break
luminosities reduce the contribution of intermediate-brightness AGN to
the LyC emissivity .  We find that the LyC emissivity peaks at $z\sim
2$.  We derive the average hydrogen photoionization rate by filtering
the hydrogen-ionizing emissivity through the intergalactic \HI\ column
density distribution.  We find that the HI photoionization rate is
lower than that required by the Lyman-$\alpha$ forest data at $z>2$.
Our hydrogen photoionization rate estimates are also considerably
lower (by a factor of 10) than that of \citet{2015AA...578A..83G}.
This indicates that hydrogen reionization is unlikely to have caused
by AGN alone.  Extrapolating the \HI\ column density distribution
function to $z>3.5$, we find that even when AGN down to $M_{1450}=-18$
are assumed to supply hydrogen-ionizing photons with a unit escape
fraction, the resultant photoionization rate is only about 10\% of
what is observed at $z\sim 6$.  At the lowest redshifts ($z\sim 0$),
we find that the hydrogen photoionization rate is about a factor of
two higher than the estimate of \citet{2007ApJ...654..731H} and
\citet{2012ApJ...746..125H}.  When compared with the recent analysis
of \citet{2017MNRAS.467.3172G}, this photoionisation rate appears to
alleviate the photon underproduction crisis
\citep{2014ApJ...789L..32K}.  Helium reionization in our model occurs
at redshift $z=3.2$ or $z=3.5$ if the luminosity function is
integrated down to $M_{1450}=-21$ and $-18$, respectively.

>>>>

\documentclass[fleqn,usenatbib]{mnras}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx}	
\usepackage{amsmath}	
\usepackage{amssymb}
\usepackage{pdflscape}
\usepackage{siunitx}
\def\lya{Ly$\alpha$~}
\usepackage{color}
\definecolor{notecolor}{rgb}{0.8,0,0}
\newcommand{\gk}[1]{{\bf \color{notecolor} [#1]}}
\def\HI{\hbox{H~$\scriptstyle\rm I$}}
\def\HII{\hbox{H~$\scriptstyle\rm II$}}
\def\nHI{{\rm HI}}
\def\nH{{\rm H}}
\def\nHII{{\rm HII}}
\def\nHe{{\rm He}}
\def\nHeI{{\rm HeI}}
\def\nHeII{{\rm HeII}}
\def\nHeIII{{\rm HeIII}}
\def\bHII{\hbox{\bf H~$\scriptstyle\bf II$}}
\def\HeI{\hbox{He~$\scriptstyle\rm I$}}
\def\HeII{\hbox{He~$\scriptstyle\rm II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\def\bHeII{\hbox{\bf He~$\scriptstyle\bf II$}}
\def\HeIII{\hbox{He~$\scriptstyle\rm III$}}
\usepackage{dcolumn}
\newcolumntype{.}{D{.}{.}{2.7}}
\newcolumntype{e}{D{.}{.}{2.10}}
\newcolumntype{d}{D{.}{.}{2.3}}

@@

\author[Kulkarni et al.]
       {{Girish Kulkarni$^{1}$\thanks{Email: kulkarni@ast.cam.ac.uk},
           G\'abor Worseck$^{2}$
           and Joseph F.~Hennawi$^{3}$} \\
         $^1$Institute of Astronomy and Kavli Institute of Cosmology,
         University of Cambridge, Madingley Road, Cambridge CB3 0HA,
         UK \\
         $^2$Institute f\"ur Physik und Astronomie, Universit\"at
         Potsdam, Karl-Liebknecht-Stra\ss e\ 24/25, 14476 Potsdam,
         Germany \\
         $^3$Department of Physics, Broida Hall, UC Santa Barbara,
         Santa Barbara, CA 93106-9530 USA}
       \date{Accepted ---. Received ---; in original form ---}

@@

\begin{abstract}
  Determinations of the UV luminosity function of AGN at high
  redshifts are important for constraining the contribution of AGN to
  reionization.  Many recent inferences of the luminosity function
  suffer from inconsistencies arising from inhomogeneous selection and
  mixing of AGN data.  We address this problem in this paper by
  constructing a sample of more than 85,000 colour-selected AGN from
  redshift $z=0$ to $7.5$.  This sample is constructed out of multiple
  data sets with spectroscopic redshifts and completeness estimates.
  We homogenise these data sets to identical cosmologies, intrinsic
  AGN spectra, and magnitude systems.  Using this sample, we derive
  the AGN UV luminosity function from redshifts $z=0$ to $7.5$.  The
  luminosity function has a double power law form at $z<5.5$, and
  single power law form at higher redshifts.  The break luminosity
  brightens rapidly with redshift and the faint end of the luminosity
  function steepens.  In spite of this steepening, the contribution of
  AGN to the hydrogen photoionization rate at $z=5$--$6$ is
  subdominant, although it can be non-negligible if these luminosity
  functions hold down to $M_{1450}=-18$.  Under reasonable
  assumptions, AGN can reionize \HeII\ by redshift $z=3.2$.  At low
  redshifts ($z<0.5$), AGN can produce all of the hydrogen
  photoionization rate implied by the \lya data.  Our global analysis
  of the luminosity function also reveals important systematic errors
  in the data, particularly at $z<0.6$ and $z=2.2$--$3.5$, which need
  to be addressed in future in order to improve our results.  We make
  various fitting functions, luminosity function analysis codes, and
  homogenised AGN data publicly available.
\end{abstract}

@@

@@

The luminosity function of active galactic nuclei (AGN) and its
evolution over cosmological time scales has been a matter of central
interest of a large body of work over the last four decades
\citep[e.g.,][]{1978A&A....68...17M, 1983ApJ...269..352S,
  1988ApJ...325...92K, 1988MNRAS.235..935B, 1993ApJ...406L..43H,
  1994ApJ...421..412W, 1995AJ....110...68S, 1995AJ....110.2553K,
  1995ApJ...438..623P, 2000MNRAS.317.1014B, 2001AJ....121...54F,
  2004AJ....128..515F, 2006AJ....131.2766R, 2007ApJ...654..731H,
  2009MNRAS.392...19C, 2010AJ....139..906W, 2011ApJ...728L..26G,
  2013ApJ...773...14R, 2013ApJ...768..105M, 2015AA...578A..83G,
  2015ApJ...798...28K, 2016ApJ...829...33Y, 2016ApJ...833..222J,
  2017MNRAS.466.1160M}.  Determination of the AGN luminosity function
constrains models of the build-up of supermassive black holes
\citep{2015MNRAS.452..575S, 2016MNRAS.462..190R}.  Due to the
incidence of supermassive black holes in most galaxies, the tight
scaling relations observed to exist between the mass of these black
holes and properties of their host galaxies
\citep{2013ARA&A..51..511K, 2013ApJ...764..184M}, and the increasing
consensus that AGN activity feeds back on the host galaxy evolution,
the AGN luminosity function also constrains models of galaxy
formation.  Finally, thanks to their relative brightness and high
Lyman-continuum (LyC) escape fractions, the luminosity function of AGN
determines their influence on the temperature and ionization state of
the intergalactic medium (IGM) over large scales, possibly even
primarily driving hydrogen and helium reionization.

There is a renewed interest in understanding the evolution of the UV
luminosity function of AGN, triggered by the 19 low-luminosity
($M_{1450}>-22.6$) AGN candidates between redshifts $z=4.1$ and $6.3$
discovered by \citet{2015AA...578A..83G} using a novel X-ray/NIR
selection criterion.  This finding suggested that AGN brighter than
$M_{1450}=-18$ can potentially produce all of the metagalactic
hydrogen photoionization rate inferred from the \lya forest at
$4<z<6$.  A significant presence of AGN at high redshift ($z\sim 6$)
and a dominant contribution of AGN to reionization is appealing as the
LyC escape fraction of galaxies is uncertain.  High-redshift galaxies
down to rest-frame UV magnitude $M_\mathrm{UV}=-12.5$ ($L\sim
10^{-3}L^*$) at $z=6$ \citep{2017ApJ...835..113L} and redshifts up to
$z=11.1$ \citep{2016ApJ...819..129O} have now been reported.  But the
escape of LyC photons has been measured in only a few comparatively
bright ($L>0.5L^*$) galaxies at relatively low redshifts ($z < 4$).
The escape fraction in these galaxies is inferred to be typically
about 2--20\% \citep{2010ApJ...725.1011V, 2011ApJ...736...41B,
  2015ApJ...804...17S, 2015ApJ...810..107M, 2016A&A...585A..48G,
  2017MNRAS.468..389J, 2017MNRAS.465..316M}, whereas reionization
requires escape fraction of about 20\% in galaxies as faint as
$M_\mathrm{UV}=-13$ \citep{2016PASA...33...37F, 2015ApJ...802L..19R,
  2016MNRAS.457.4051K}.  An enhanced incidence of high-redshift AGN
may also be consistent with the shallow bright-end slopes of the
$z\sim 7$ UV luminosity function of galaxies relative to a Schechter
function \citep{2012MNRAS.426.2772B, 2014MNRAS.440.2810B,
  2014ApJ...792...76B, 2015MNRAS.452.1817B} and the hard spectra of
these galaxies \citep{2015MNRAS.450.1846S, 2015MNRAS.454.1393S,
  2017MNRAS.464..469S}.  Finally, AGN may also provide a natural
explanation for the large scatter in the \lya opacity between
different quasar sightlines close to redshift $z=6$
\citep{2015MNRAS.447.3402B, 2018arXiv180208177B}.  These opacity
fluctuations extend to substantially larger scales ($\gtrsim 50\,
h^{-1}$cMpc) than expected in galaxies-dominated reionization models
\citep{2015MNRAS.453.2943C}.  AGN clustering can result in these
fluctuations naturally if there is a significant contribution
($\gtrsim 50\%$) of AGN to the ionising emissivity at $z=5$--$6$
\citep{2017MNRAS.465.3429C}.

Several counter-arguements against a higher incidence of AGN at high
redshift have also been made. \citet{2017MNRAS.468.4691D} and
\citet{2018MNRAS.473.1416M} pointed out that an AGN population
consistent with the findings of \citet{2015AA...578A..83G} leads to a
much earlier \HeII\ reionization.  For instance, in the model of
\citet{2015ApJ...813L...8M}, He~\textsc{ii} reionization is complete
at $z=4.5$, compared to $z=3$ in the standard scenario
\citep{2012ApJ...746..125H}.  Such early \HeII\ reionization could
result in higher IGM temperatures due to the associated photoheating.
\citet{2017MNRAS.468.4691D} found that the temperature of the IGM at
mean density is twice as much in AGN-dominated reionization models as
the standard models at $z=3.5$--$5$, in conflict with constraints from
the \lya forest.  This inconsistency could be avoided by postulating a
reduced escape fraction of \HeII-ionizing photons in AGN, but it is
difficult to reconcile this with a unit escape fraction of
hydrogen-ionizing photons that is required to explain the Ly$\alpha$
opacity fluctuations.  Further arguments against AGN-dominated
reionization have been presented by \citet{2016MNRAS.459.2299F} by
analysing the incidence of metal-line absorbers at $z\sim 6$.
\citet{2016MNRAS.459.2299F} find that in their cosmological radiation
hydrodynamical simulations AGN-dominated UV background results in too
many C~\textsc{iv} absorption systems relative to Si~\textsc{iv} and
C~\textsc{ii} at $z\sim 6$.  However, these simulations assume a
$L_\nu\propto\nu^{-1.57}$ AGN SED at extreme UV
\citep{2002ApJ...579..500T}, which somewhat harder than recent
measurements ($L_\nu\propto\nu^{-1.7}$) by
\citet{2015MNRAS.449.4204L}.  \citet{2016MNRAS.459.2299F} also found
that the N(Si~\textsc{iv})/N(C~\textsc{iv}) column density ratio
measurements prefer a harder and more intense $>4$~Ry background than
the standard model \citep{2012ApJ...746..125H}.  Finally, comparing
the \citet{2015AA...578A..83G} sample to X-ray-selected quasar data at
$z=0$--$6$, \citet{2017MNRAS.465.1915R} argued that the faint end of
the AGN UV luminosity function at $z\sim 6$ is probably shallower that
that reported by \citet{2015AA...578A..83G}.
\citet{2017MNRAS.465.1915R} argue that the apparent contradiction with
the results of \citet{2015AA...578A..83G} could be explained by
contamination from the AGN host galaxies for faint AGN.

While a straightforward way towards a more robust understanding of AGN
contribution to reionization is to determine the evolution of the AGN
UV luminosity function, many recent inferences of the luminosity
function suffer from inconsistencies arising from inhomogeneous
selection and mixing of AGN data.  This has resulted in a large
scatter in the inferred high-redshift hydrogen-ionizing AGN emissivity
between various recent studies.  For instance, there is an order of
magnitude scatter between various estimates of the hydrogen-ionizing
AGN emissivity at $z=5$--$6$ \citep{2011ApJ...728L..26G,
  2012ApJ...755..169M, 2015AA...578A..83G, 2018PASJ...70S..34A,
  2018AJ....155..131M, 2018MNRAS.474.2904P, 2017ApJ...847L..15O,
  2017MNRAS.466.1160M}.  Our aim in this paper is to address this
issue, by constructing an AGN sample with robust redshift and
completeness estimates and homogeneous assumptions of the cosmology
and intrinsic AGN spectrum.  We discuss our sample construction in
Section~\ref{sec:sample}.  Our derived luminosity functions are
presented in Section~\ref{sec:lf}.  Section~\ref{sec:reion} presents
our inference of the AGN contribution to hydrogen and helium
reionization.  We summarise our findings in Section~\ref{sec:conc}.

@@

\section{Luminosity function}
\label{sec:lf}

@@

      \begin{table}
        \caption{Best-fit luminosity function evolution models.  These
          parameters are defined in Equations~(\ref{eqn:cbs}) and
          (\ref{eqn:beta}).  See Section~\ref{sec:global} for further
          details and the redshift range of validity of these models.
          Errors indicate one-sigma (68.26\%) uncertainties.  Model 2 is our
          preferred model.}
        \label{tab:global}
        \begin{tabular}{p{1.0cm}eee}
          \hline 
          Param. &
          \multicolumn{1}{c}{Model 1} &
          \multicolumn{1}{c}{Model 2} &
          \multicolumn{1}{c}{Model 3} \\
          \hline
          $c_{0,0}$ & -7.559^{+0.131}_{-0.139} & -7.084^{+0.136}_{-0.142} & -6.842^{+0.077}_{-0.076} \\     
          $c_{0,1}$ & 1.013^{+0.079}_{-0.072} & 0.753^{+0.080}_{-0.073} & 0.590^{+0.039}_{-0.041} \\        
          $c_{0,2}$ & -0.113^{+0.005}_{-0.005} & -0.096^{+0.004}_{-0.005} & -0.083^{+0.003}_{-0.003} \\
          \\
          $c_{1,0}$ & -17.006^{+0.230}_{-0.243} & -15.423^{+0.263}_{-0.261} & -15.140^{+0.144}_{-0.136} \\  
          $c_{1,1}$ & -5.548^{+0.156}_{-0.143} & -6.725^{+0.156}_{-0.171} & -6.910^{+0.091}_{-0.093} \\     
          $c_{1,2}$ & 0.588^{+0.016}_{-0.019} & 0.737^{+0.018}_{-0.015} & 0.750^{+0.012}_{-0.013} \\        
          $c_{1,3}$ & -0.023^{+0.001}_{-0.001} & -0.029^{+0.001}_{-0.001} & -0.029^{+0.001}_{-0.001} \\
          \\
          $c_{2,0}$ & -3.246^{+0.121}_{-0.123} & -2.973^{+0.117}_{-0.133} & -2.950^{+0.105}_{-0.097} \\     
          $c_{2,1}$ & -0.250^{+0.048}_{-0.050} & -0.347^{+0.050}_{-0.050} & -0.363^{+0.040}_{-0.043} \\
          \\
          $c_{3,0}$ & -2.350^{+0.051}_{-0.060} & -2.545^{+0.123}_{-0.290} & -1.424^{+0.031}_{-0.031} \\     
          $c_{3,1}$ & 0.647^{+0.072}_{-0.060} & 1.581^{+0.520}_{-0.264} & -0.111^{+0.010}_{-0.010} \\       
          $c_{3,2}$ & 3.857^{+0.092}_{-0.073} & 2.102^{+0.450}_{-0.283} & \multicolumn{1}{c}{---} \\        
          $c_{3,3}$ & 27.534^{+41.364}_{-9.405} & 1.965^{+0.461}_{-0.464} & \multicolumn{1}{c}{---} \\      
          $c_{3,4}$ & -0.002^{+0.074}_{-0.082} & -0.641^{+0.169}_{-0.154} & \multicolumn{1}{c}{---} \\      
          \hline 
        \end{tabular}
      \end{table}

      \section{Contribution of AGN to reionization}
      \label{sec:reion}

@@

      \section{Conclusions}
      \label{sec:conc}

@@

      In spite of the rapid steepening of the faint end of the luminosity
      function at high redshifts, our derived hydrogen-ionizing emissivity
      from AGN is lower that recent determinations from the literature
      \citep{2015AA...578A..83G}.  This is because the bright break
      luminosities reduce the contribution of intermediate-brightness AGN to
      the LyC emissivity.  We find that the LyC emissivity peaks at $z\sim
      2$.  We derive the average hydrogen photoionization rate by filtering
      the hydrogen-ionizing emissivity through the intergalactic \HI\ column
      density distribution.  We find that the HI photoionization rate is
      lower than that required by the Lyman-$\alpha$ forest data at $z>2$.
      Our hydrogen photoionization rate estimates are also considerably
      lower (by a factor of 10) than that of \citet{2015AA...578A..83G}.
      This indicates that hydrogen reionization is unlikely to have caused
      by AGN alone.  Extrapolating the \HI\ column density distribution
      function to $z>3.5$, we find that even when AGN down to $M_{1450}=-18$
      are assumed to supply hydrogen-ionizing photons with a unit escape
      fraction, the resultant photoionization rate is only about 10\% of
      what is observed at $z\sim 6$.  At the lowest redshifts ($z\sim 0$),
      we find that the hydrogen photoionization rate is about a factor of
      two higher than the estimate of \citet{2007ApJ...654..731H} and
      \citet{2012ApJ...746..125H}.  When compared with the recent analysis
      of \citet{2017MNRAS.467.3172G}, this photoionisation rate appears to
      alleviate the photon underproduction crisis
      \citep{2014ApJ...789L..32K}.  Helium reionization in our model occurs
      at redshift $z=3.2$ or $z=3.5$ if the luminosity function is
      integrated down to $M_{1450}=-21$ and $-18$, respectively.
